ppseq: An R Package for Sequential Predictive Probability Monitoring

### 2021-08-27 inst/ppseq-package-paper/zabor-hobbs-kane.Rmd
updating R Journal paper with new datasets

Next we print the results table using the \code{print()} option, and limited to designs with type I error between 0.01 and 0.2, and a minimum power of 0.7. We find that 35 of the 76 designs meet these criteria for type I error and power.

```{r}
print(
  one_sample_cal_tbl,
  type1_range = c(0.01, 0.2),
  minimum_power = 0.7
  )
```

@@

```{r eval = FALSE}
plot(
  one_sample_cal_tbl, 
  type1_range = c(0.01, 0.2), 
  minimum_power = 0.7,
  plotly = TRUE
  )
```

```{r echo = FALSE, fig.width = 6, fig.height = 4, include = knitr::is_latex_output(), eval = knitr::is_latex_output(), fig.cap = "Plot of design options made with ggplot. The color represents the Euclidean distance to the top left point and the optimal design is indicated by a diamond."}
p <- plot(
  one_sample_cal_tbl,
  type1_range = c(0.01, 0.2),
  minimum_power = 0.7,
  plotly = FALSE
  )
p
```

```{r echo = FALSE, fig.width = 6, fig.height = 4, include=knitr::is_html_output(), eval=knitr::is_html_output(), fig.cap = "Plot of design options made with plotly. The color represents the Euclidean distance to the top left point and the optimal design is indicated by a diamond."}
p <- plot(
  one_sample_cal_tbl,
  type1_range = c(0.01, 0.2),
  minimum_power = 0.7,
  plotly = TRUE
  )
p[[1]]
p[[2]]
```

@@

```{r message = FALSE, fig.height = 8, fig.width = 6, include = knitr::is_latex_output(), eval = knitr::is_latex_output(), fig.cap = "Plot of decision rules made with ggplot. The color indicates whether the trial should stop or proceed for a given number of responses at each interim analysis."}
plot(one_sample_decision_tbl, plotly = FALSE)
```

```{r message = FALSE, fig.height = 8, fig.width = 6, include=knitr::is_html_output(), eval=knitr::is_html_output(), fig.cap = "Plot of decision rules made with plotly. The color indicates whether the trial should stop or proceed for a given number of responses at each interim analysis."}
plot(one_sample_decision_tbl)
```

>>>>

Next we print the results table using the \code{print()} option, and limited to designs with type I error between 0.05 and 0.1, and a minimum power of 0.7. We find that 35 of the 76 designs meet these criteria for type I error and power.

```{r}
print(
  one_sample_cal_tbl,
  type1_range = c(0.05, 0.1),
  minimum_power = 0.7
  )
```

@@

```{r eval = FALSE}
plot(
  one_sample_cal_tbl, 
  type1_range = c(0.05, 0.1), 
  minimum_power = 0.7,
  plotly = TRUE
  )
```

```{r echo = FALSE, fig.width = 6, fig.height = 4, include = knitr::is_latex_output(), eval = knitr::is_latex_output(), fig.cap = "Plot of design options made with ggplot. The color represents the Euclidean distance to the top left point and the optimal design is indicated by a diamond."}
p <- plot(
  one_sample_cal_tbl,
  type1_range = c(0.05, 0.1),
  minimum_power = 0.7,
  plotly = FALSE
  )
p
```

```{r echo = FALSE, fig.width = 6, fig.height = 4, include=knitr::is_html_output(), eval=knitr::is_html_output(), fig.cap = "Plot of design options made with plotly. The color represents the Euclidean distance to the top left point and the optimal design is indicated by a diamond."}
p <- plot(
  one_sample_cal_tbl,
  type1_range = c(0.05, 0.1),
  minimum_power = 0.7,
  plotly = TRUE
  )
p[[1]]
p[[2]]
```

@@

```{r message = FALSE, fig.height = 9, fig.width = 6, include = knitr::is_latex_output(), eval = knitr::is_latex_output(), fig.cap = "Plot of decision rules made with ggplot. The color indicates whether the trial should stop or proceed for a given number of responses at each interim analysis."}
plot(one_sample_decision_tbl, plotly = FALSE)
```

```{r message = FALSE, fig.height = 9, fig.width = 6, include=knitr::is_html_output(), eval=knitr::is_html_output(), fig.cap = "Plot of decision rules made with plotly. The color indicates whether the trial should stop or proceed for a given number of responses at each interim analysis."}
plot(one_sample_decision_tbl)
```
